---
title: "R Notebook"
output: html_notebook
---

```{r, echo=FALSE}
library(tseries)
library(lawstat)
library(forecast)
library(hydroGOF)
library(vars)
```

## 1. Data Exploration
### Read in the dataset
```{r}
setwd("~/Dropbox/MSAN/module2/msan604/group_project")
train <- read.csv('train.csv')[-1] # use -1 index to take out the month variable because
                                   # we will recreate the month variable using ts() function
test <- read.csv('test.csv')[-1]
plot(train)
cor(train)
```
Summary: from the plot and the correlation matrix, unemployment rate and house price index are most correlated to bankruptcy. However, population and house price index are are highly correlated with each other. This suggests that in the modeling part, we should use either of the external variable. For now, Let's focus on the bankruptcy variable only.

### Create training sets for each of the variable except for population, because population exhibits an upward trend that doesn't contribute to explaining the variance in bankruptcy
```{r}
bank <- train[3]
hpi <- train[4]
unemp <- train[1]

hpi2 <- test[3]
unemp2 <- test[1]

bank_train <- ts(bank, start = c(1987, 1), frequency = 12)
hpi_train <- ts(hpi, start = c(1987, 1), frequency = 12)
unemp_train <- ts(unemp, start = c(1987, 1), frequency = 12)

hpi_test <- ts(hpi2, start = c(2011, 1), frequency = 12)
unemp_test <- ts(unemp2, start = c(2011, 1), frequency = 12)

hpi_unemp_train <- ts(data.frame(hpi, unemp), start = c(1987, 1), frequency = 12)
plot(bank_train)
plot(hpi_train)
plot(unemp_train)
```


### plot the raw data as well as acf and pacf plots
```{r}
par(mfrow=c(3,1))
plot(bank_train)
acf(bank_train, lag.max = 48)
pacf(bank_train, lag.max = 48)
```
Summary: From the ACF plot and the PACF plot there is surely trend in the time series. There seems to be seasonality, but it's not significant.

### Use ndiff and ndiffs to automatically check the number of ordinary and seasonal differencing
```{r}
ndiffs(bank_train, max.d = 3)
nsdiffs(bank_train, m = 12, max.D = 2)
adf.test(bank_train)
```
Summary: Seems that we dont need seasonal differencing, however it's good to try both.

### Use both ordinary and seasonal differencing and plot ACF and PACF
```{r}
# We need to use order 1 ordinary difference
bank_train.diff <- diff(bank_train)
bank_train.diff12 <- diff(bank_train.diff, lag = 12)
adf.test(bank_train.diff)
adf.test(bank_train.diff12)

plot(bank_train.diff)
acf(bank_train.diff, lag.max = 48)
pacf(bank_train.diff, lag.max = 48)

plot(bank_train.diff12)
acf(bank_train.diff12, lag.max = 48)
pacf(bank_train.diff12, lag.max = 48)


# We need to use order 1 ordinary difference
bank_train.diff <- diff(log(bank_train))
bank_train.diff12 <- diff(bank_train.diff, lag = 12)
adf.test(bank_train.diff)
adf.test(bank_train.diff12)

plot(bank_train.diff)
acf(bank_train.diff, lag.max = 48)
pacf(bank_train.diff, lag.max = 48)

plot(bank_train.diff12)
acf(bank_train.diff12, lag.max = 48)
pacf(bank_train.diff12, lag.max = 48)
```
Summary: After differencing, the result of the Dick-Fuller test indicates that the trend has been removed. Based on the ACF and PACF plots for the ordinarily differenced data, it seems that p = q = 2, P = 1, Q = 2. Also we choose d = 1, D = 0 or 1. Next, let's try out the combinations of the parameters and choose an optimal model.

## 2. Modeling
### 2.1 Models without Exogenous Variables
#### Train the model not using seasonal differencing
```{r}
m1 <- arima(log(bank_train), order = c(0,1,1), seasonal = list(order = c(1,0,2), period = 12), method='ML')
m2 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(1,0,2), period = 12), method='ML')
m3 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(1,0,2), period = 12), method='ML')
m4 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(2,0,2), period = 12), method='ML')
m5 <- arima(log(bank_train), order = c(0,1,1), seasonal = list(order = c(1,0,1), period = 12), method='ML')
m6 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(1,0,1), period = 12), method='ML')
m7 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,0,1), period = 12), method='ML')
m8 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,0,2), period = 12), method='ML')
m9 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(2,0,2), period = 12), method='ML')
m10 <- arima(log(bank_train), order = c(1,1,2), seasonal = list(order = c(1,0,1), period = 12), method='ML')
m11 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,0,2), period = 12), method='ML')
m12 <- arima(log(bank_train), order = c(1,1,0), seasonal = list(order = c(1,0,2), period = 12), method='ML')
m13 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,0,1), period = 12), method='ML')
m14 <- arima(log(bank_train), order = c(1,1,0), seasonal = list(order = c(1,0,1), period = 12), method='ML')
m15 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(1,0,1), period = 12), method='ML')
m16 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(2,0,1), period = 12), method='ML')
m17 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(2,0,2), period = 12), method='ML')
m18 <- arima(log(bank_train), order = c(2,1,0), seasonal = list(order = c(1,0,2), period = 12), method='ML')
m19 <- arima(log(bank_train), order = c(2,1,1), seasonal = list(order = c(1,0,1), period = 12), method='ML')
m20 <- arima(log(bank_train), order = c(2,1,0), seasonal = list(order = c(1,0,1), period = 12), method='ML')
m21 <- arima(log(bank_train), order = c(2,1,1), seasonal = list(order = c(1,0,2), period = 12), method='ML')
m22 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(1,0,2), period = 12), method='ML')
sigma2<-c(m1$sigma2,m2$sigma2,m3$sigma2,m4$sigma2,m5$sigma2,m6$sigma2,m7$sigma2,m8$sigma2,m9$sigma2,m10$sigma2,m11$sigma2,m12$sigma2,m13$sigma2,m14$sigma2,m15$sigma2,m16$sigma2, m17$sigma2,m18$sigma2,m19$sigma2, m20$sigma2,m21$sigma2,m22$sigma2)
loglik<-c(m1$loglik,m2$loglik,m3$loglik,m4$loglik,m5$loglik,m6$loglik,m7$loglik,m8$loglik,m9$loglik,m10$loglik,m11$loglik,m12$loglik,m13$loglik,m14$loglik,m15$loglik,m16$loglik, m17$loglik,m18$loglik,m19$loglik, m20$loglik,m21$loglik,m22$loglik)
AIC<-c(m1$aic,m2$aic,m3$aic,m4$aic,m5$aic,m6$aic,m7$aic,m8$aic,m9$aic,m10$aic,m11$aic,m12$aic,m13$aic,m14$aic,m15$aic,m16$aic, m17$aic,m18$aic,m19$aic, m20$aic,m21$aic,m22$aic)
d <- data.frame(sigma2,loglik,AIC)
d
```

#### Train the model using seasonal differencing
```{r}
m1 <- arima(log(bank_train), order = c(0,1,1), seasonal = list(order = c(1,1,2), period = 12))
m2 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(1,1,2), period = 12))
m3 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(1,1,2), period = 12))
m4 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(2,1,2), period = 12))
m5 <- arima(log(bank_train), order = c(0,1,1), seasonal = list(order = c(1,1,1), period = 12))
m6 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(1,1,1), period = 12))
m7 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,1,1), period = 12))
m8 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,1,2), period = 12))
m9 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(2,0,2), period = 12))
m10 <- arima(log(bank_train), order = c(1,1,2), seasonal = list(order = c(1,1,1), period = 12))
m11 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,1,2), period = 12))
m12 <- arima(log(bank_train), order = c(1,1,0), seasonal = list(order = c(1,1,2), period = 12))
m13 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,1,1), period = 12))
m14 <- arima(log(bank_train), order = c(1,1,0), seasonal = list(order = c(1,1,1), period = 12))
m15 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(1,1,1), period = 12))
m16 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(2,0,1), period = 12))
m17 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(2,1,2), period = 12))
m18 <- arima(log(bank_train), order = c(2,1,0), seasonal = list(order = c(1,1,2), period = 12))
m19 <- arima(log(bank_train), order = c(2,1,1), seasonal = list(order = c(1,1,1), period = 12))
m20 <- arima(log(bank_train), order = c(2,1,0), seasonal = list(order = c(1,1,1), period = 12))
m21 <- arima(log(bank_train), order = c(2,1,1), seasonal = list(order = c(1,1,2), period = 12))
m22 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(1,0,2), period = 12))
sigma2<-c(m1$sigma2,m2$sigma2,m3$sigma2,m4$sigma2,m5$sigma2,m6$sigma2,m7$sigma2,m8$sigma2,m9$sigma2,m10$sigma2,m11$sigma2,m12$sigma2,m13$sigma2,m14$sigma2,m15$sigma2,m16$sigma2, m17$sigma2,m18$sigma2,m19$sigma2, m20$sigma2,m21$sigma2,m22$sigma2)
loglik<-c(m1$loglik,m2$loglik,m3$loglik,m4$loglik,m5$loglik,m6$loglik,m7$loglik,m8$loglik,m9$loglik,m10$loglik,m11$loglik,m12$loglik,m13$loglik,m14$loglik,m15$loglik,m16$loglik, m17$loglik,m18$loglik,m19$loglik, m20$loglik,m21$loglik,m22$loglik)
AIC<-c(m1$aic,m2$aic,m3$aic,m4$aic,m5$aic,m6$aic,m7$aic,m8$aic,m9$aic,m10$aic,m11$aic,m12$aic,m13$aic,m14$aic,m15$aic,m16$aic, m17$aic,m18$aic,m19$aic, m20$aic,m21$aic,m22$aic)
d <- data.frame(sigma2,loglik,AIC)
d
```

### 2.2 Models with House Price Index as exogenous variable without Seasonal Differencing
```{r}
m1 <- arima(log(bank_train), order = c(0,1,1), seasonal = list(order = c(1,0,2), period = 12),  xreg = log(hpi_train))
m2 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(1,0,2), period = 12),  xreg = log(hpi_train))
m3 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(1,0,2), period = 12),  xreg = log(hpi_train))
m4 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(2,0,2), period = 12),  xreg = log(hpi_train))
m5 <- arima(log(bank_train), order = c(0,1,1), seasonal = list(order = c(1,0,1), period = 12),  xreg = log(hpi_train))
m6 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(1,0,1), period = 12),  xreg = log(hpi_train))
m7 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,0,1), period = 12),  xreg = log(hpi_train))
m8 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,0,2), period = 12),  xreg = log(hpi_train))
m9 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(2,0,2), period = 12),  xreg = log(hpi_train))
m10 <- arima(log(bank_train), order = c(1,1,2), seasonal = list(order = c(1,0,1), period = 12),  xreg = log(hpi_train))
m11 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,0,2), period = 12),  xreg = log(hpi_train))
m12 <- arima(log(bank_train), order = c(1,1,0), seasonal = list(order = c(1,0,2), period = 12),  xreg = log(hpi_train))
m13 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,0,1), period = 12),  xreg = log(hpi_train))
m14 <- arima(log(bank_train), order = c(1,1,0), seasonal = list(order = c(1,0,1), period = 12),  xreg = log(hpi_train))
m15 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(1,0,1), period = 12),  xreg = log(hpi_train))
m16 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(2,0,1), period = 12),  xreg = log(hpi_train))
m17 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(2,0,2), period = 12),  xreg = log(hpi_train))
m18 <- arima(log(bank_train), order = c(2,1,0), seasonal = list(order = c(1,0,2), period = 12),  xreg = log(hpi_train))
m19 <- arima(log(bank_train), order = c(2,1,1), seasonal = list(order = c(1,0,1), period = 12),  xreg = log(hpi_train))
m20 <- arima(log(bank_train), order = c(2,1,0), seasonal = list(order = c(1,0,1), period = 12),  xreg = log(hpi_train))
m21 <- arima(log(bank_train), order = c(2,1,1), seasonal = list(order = c(1,0,2), period = 12),  xreg = log(hpi_train))
m22 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(1,0,2), period = 12),  xreg = log(hpi_train))
sigma2<-c(m1$sigma2,m2$sigma2,m3$sigma2,m4$sigma2,m5$sigma2,m6$sigma2,m7$sigma2,m8$sigma2,m9$sigma2,m10$sigma2,m11$sigma2,m12$sigma2,m13$sigma2,m14$sigma2,m15$sigma2,m16$sigma2, m17$sigma2,m18$sigma2,m19$sigma2, m20$sigma2,m21$sigma2,m22$sigma2)
loglik<-c(m1$loglik,m2$loglik,m3$loglik,m4$loglik,m5$loglik,m6$loglik,m7$loglik,m8$loglik,m9$loglik,m10$loglik,m11$loglik,m12$loglik,m13$loglik,m14$loglik,m15$loglik,m16$loglik, m17$loglik,m18$loglik,m19$loglik, m20$loglik,m21$loglik,m22$loglik)
AIC<-c(m1$aic,m2$aic,m3$aic,m4$aic,m5$aic,m6$aic,m7$aic,m8$aic,m9$aic,m10$aic,m11$aic,m12$aic,m13$aic,m14$aic,m15$aic,m16$aic, m17$aic,m18$aic,m19$aic, m20$aic,m21$aic,m22$aic)
d <- data.frame(sigma2,loglik,AIC)
d
```

### 2.3 Models with Umemployment Rate as Exogenous Variable without Seasonal Differencing
```{r}
m1 <- arima(log(bank_train), order = c(0,1,1), seasonal = list(order = c(1,0,2), period = 12), xreg = log(unemp_train))
m2 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(1,0,2), period = 12), xreg = log(unemp_train))
m3 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(1,0,2), period = 12), xreg = log(unemp_train))
m4 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(2,0,2), period = 12), xreg = log(unemp_train))
m5 <- arima(log(bank_train), order = c(0,1,1), seasonal = list(order = c(1,0,1), period = 12), xreg = log(unemp_train))
m6 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(1,0,1), period = 12), xreg = log(unemp_train))
m7 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,0,1), period = 12), xreg = log(unemp_train))
m8 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,0,2), period = 12), xreg = log(unemp_train))
m9 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(2,0,2), period = 12), xreg = log(unemp_train))
m10 <- arima(log(bank_train), order = c(1,1,2), seasonal = list(order = c(1,0,1), period = 12), xreg = log(unemp_train))
m11 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,0,2), period = 12), xreg = log(unemp_train))
m12 <- arima(log(bank_train), order = c(1,1,0), seasonal = list(order = c(1,0,2), period = 12), xreg = log(unemp_train))
m13 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,0,1), period = 12), xreg = log(unemp_train))
m14 <- arima(log(bank_train), order = c(1,1,0), seasonal = list(order = c(1,0,1), period = 12), xreg = log(unemp_train))
m15 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(1,0,1), period = 12), xreg = log(unemp_train))
m16 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(2,0,1), period = 12), xreg = log(unemp_train))
m17 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(2,0,2), period = 12), xreg = log(unemp_train))
m18 <- arima(log(bank_train), order = c(2,1,0), seasonal = list(order = c(1,0,2), period = 12), xreg = log(unemp_train))
m19 <- arima(log(bank_train), order = c(2,1,1), seasonal = list(order = c(1,0,1), period = 12), xreg = log(unemp_train))
m20 <- arima(log(bank_train), order = c(2,1,0), seasonal = list(order = c(1,0,1), period = 12), xreg = log(unemp_train))
m21 <- arima(log(bank_train), order = c(2,1,1), seasonal = list(order = c(1,0,2), period = 12), xreg = log(unemp_train))
m22 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(1,0,2), period = 12), xreg = log(unemp_train))
sigma2<-c(m1$sigma2,m2$sigma2,m3$sigma2,m4$sigma2,m5$sigma2,m6$sigma2,m7$sigma2,m8$sigma2,m9$sigma2,m10$sigma2,m11$sigma2,m12$sigma2,m13$sigma2,m14$sigma2,m15$sigma2,m16$sigma2, m17$sigma2,m18$sigma2,m19$sigma2, m20$sigma2,m21$sigma2,m22$sigma2)
loglik<-c(m1$loglik,m2$loglik,m3$loglik,m4$loglik,m5$loglik,m6$loglik,m7$loglik,m8$loglik,m9$loglik,m10$loglik,m11$loglik,m12$loglik,m13$loglik,m14$loglik,m15$loglik,m16$loglik, m17$loglik,m18$loglik,m19$loglik, m20$loglik,m21$loglik,m22$loglik)
AIC<-c(m1$aic,m2$aic,m3$aic,m4$aic,m5$aic,m6$aic,m7$aic,m8$aic,m9$aic,m10$aic,m11$aic,m12$aic,m13$aic,m14$aic,m15$aic,m16$aic, m17$aic,m18$aic,m19$aic, m20$aic,m21$aic,m22$aic)
d <- data.frame(sigma2,loglik,AIC)
d
```

### 2.4 Models with Both House Price Index and Unemployment Rate as Exogenous Variables
#### Train the model not using seasonal differencing but using both exogenous variable
```{r}
m1 <- arima(log(bank_train), order = c(0,1,1), seasonal = list(order = c(1,0,2), period = 12), xreg = log(hpi_unemp_train))
m2 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(1,0,2), period = 12), xreg = log(hpi_unemp_train))
m3 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(1,0,2), period = 12), xreg = log(hpi_unemp_train))
m4 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(2,0,2), period = 12), xreg = log(hpi_unemp_train))
m5 <- arima(log(bank_train), order = c(0,1,1), seasonal = list(order = c(1,0,1), period = 12), xreg = log(hpi_unemp_train))
m6 <- arima(log(bank_train), order = c(0,1,0), seasonal = list(order = c(1,0,1), period = 12), xreg = log(hpi_unemp_train))
m7 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,0,1), period = 12), xreg = log(hpi_unemp_train))
m8 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,0,2), period = 12), xreg = log(hpi_unemp_train))
m9 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(2,0,2), period = 12), xreg = log(hpi_unemp_train))
m10 <- arima(log(bank_train), order = c(1,1,2), seasonal = list(order = c(1,0,1), period = 12), xreg = log(hpi_unemp_train))
m11 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,0,2), period = 12), xreg = log(hpi_unemp_train))
m12 <- arima(log(bank_train), order = c(1,1,0), seasonal = list(order = c(1,0,2), period = 12), xreg = log(hpi_unemp_train))
m13 <- arima(log(bank_train), order = c(1,1,1), seasonal = list(order = c(1,0,1), period = 12), xreg = log(hpi_unemp_train))
m14 <- arima(log(bank_train), order = c(1,1,0), seasonal = list(order = c(1,0,1), period = 12), xreg = log(hpi_unemp_train))
m15 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(1,0,1), period = 12), xreg = log(hpi_unemp_train))
m16 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(2,0,1), period = 12), xreg = log(hpi_unemp_train))
m17 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(2,0,2), period = 12), xreg = log(hpi_unemp_train))
m18 <- arima(log(bank_train), order = c(2,1,0), seasonal = list(order = c(1,0,2), period = 12), xreg = log(hpi_unemp_train))
m19 <- arima(log(bank_train), order = c(2,1,1), seasonal = list(order = c(1,0,1), period = 12), xreg = log(hpi_unemp_train))
m20 <- arima(log(bank_train), order = c(2,1,0), seasonal = list(order = c(1,0,1), period = 12), xreg = log(hpi_unemp_train))
m21 <- arima(log(bank_train), order = c(2,1,1), seasonal = list(order = c(1,0,2), period = 12), xreg = log(hpi_unemp_train))
m22 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(1,0,2), period = 12), xreg = log(hpi_unemp_train))
sigma2<-c(m1$sigma2,m2$sigma2,m3$sigma2,m4$sigma2,m5$sigma2,m6$sigma2,m7$sigma2,m8$sigma2,m9$sigma2,m10$sigma2,m11$sigma2,m12$sigma2,m13$sigma2,m14$sigma2,m15$sigma2,m16$sigma2, m17$sigma2,m18$sigma2,m19$sigma2, m20$sigma2,m21$sigma2,m22$sigma2)
loglik<-c(m1$loglik,m2$loglik,m3$loglik,m4$loglik,m5$loglik,m6$loglik,m7$loglik,m8$loglik,m9$loglik,m10$loglik,m11$loglik,m12$loglik,m13$loglik,m14$loglik,m15$loglik,m16$loglik, m17$loglik,m18$loglik,m19$loglik, m20$loglik,m21$loglik,m22$loglik)
AIC<-c(m1$aic,m2$aic,m3$aic,m4$aic,m5$aic,m6$aic,m7$aic,m8$aic,m9$aic,m10$aic,m11$aic,m12$aic,m13$aic,m14$aic,m15$aic,m16$aic, m17$aic,m18$aic,m19$aic, m20$aic,m21$aic,m22$aic)
d <- data.frame(sigma2,loglik,AIC)
d
```

## 3. Forecast Bankcruptcy using House Price Index data 
### The optimal combination of p, d, q, P, D, Q should be among (2,1,1,1,0,2), (2,1,2,1,0,2), and (2,1,2,2,0,2).  
```{r}
optimal1 <- arima(log(bank_train), order = c(2,1,1), seasonal = list(order = c(1,0,2), period = 12), xreg = log(hpi_train))
optimal2 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(1,0,2), period = 12), xreg = log(hpi_train))
optimal3 <- arima(log(bank_train), order = c(2,1,2), seasonal = list(order = c(2,0,2), period = 12), xreg = log(hpi_train))
```

```{r}
fcast1 <- forecast(optimal1, h=24, x=log(hpi_test)) 
plot(fcast1, xlim = c(1987, 2013))

fcast2 <- forecast(optimal2, h=24, x=log(hpi_test)) 
plot(fcast2, xlim = c(1987, 2013))

fcast3 <- forecast(optimal3, h=24, x=log(hpi_test)) 
plot(fcast3, xlim = c(1987, 2013))
```


